---
title: "Dashboard Template"
author: "Jemma Marcus-Shi and Linjie Zhu"
date: "`r Sys.Date()`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
---

# Questions and Written Insights 

### Question 1: Students' average salary by region/state

+We will calculate the average salary for students by state or region, depending on the differences we find after analysis. The graph will show the Top 10 states with the highest average salaries.

The tab for *State by Average Salaries* shows the three states with the higest average salaries for FSB students are VA, CA, and NY, which may be more attractive for students. Thus, trying to build external relationships with the companies in these states may be more valuable and can raise more funds for the Farmer School of Business.

### Question 2: City rank by job opportunities

We will summarize the number of students employed by city and rank those cities by frequency. Thus, we can find which cities give our students the most job opportunities. It will also allow our client to be aware of which cities should be the focus of fundraising efforts. 

# State by Average Salaries {data-orientation="columns"}

```{r,echo=FALSE}
library(dplyr)
library(readr)
library(magrittr)
df <- read.csv('FSB_Survey.csv')
cities = read.csv('uscities.csv')
```

```{r,echo=FALSE}
df <- df %>% mutate(city_state = paste(survey_city, ", ", survey_state))
cities <- cities %>% mutate(city_state = toupper(paste(city, ", ", state_id)))
```

```{r,echo=FALSE}
df_final <- left_join(df, cities %>% select(city_state, lat, lng), by = "city_state")
```

```{r,echo=FALSE}
grouped_data <- df %>%
  group_by(survey_state) %>% 
  summarize(AvgSalary = mean(survey_salary),
            OfferCount = n()) %>%  
  filter(OfferCount >= 10) 
```


## Column {data-width="400"}

### Top Ten Highest Average Salaries by State

```{r,echo=FALSE}
library(ggplot2)

# Sort the grouped data by AvgSalary in descending order
grouped_data <- grouped_data %>%
  arrange(desc(AvgSalary))

# Take the top 10 states
top_10_states <- head(grouped_data, 10)

# Create a bar chart for the top 10 states
ggplot(top_10_states, aes(x = reorder(survey_state, -AvgSalary), y = AvgSalary)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(x = "State", y = "Average Salary") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
This graph above shows the three states VA, CA< and NY have the highest average salaries for Miami's graduation students, which is more attractive for students. Thus, try to build external relationships with the companies in these states may be more valuable and can raise more fund for the Farmer School of Business.

# City Rank by Number of Job Placements {data-orientation="columns"}

```{r}
offers_by_city <- df_final %>%
  group_by(city_state) %>%  
  summarize(Offer_Count = n())

ranked_offers <- offers_by_city %>%
  arrange(desc(Offer_Count)) %>%
  mutate(Rank = row_number())
```

## Column {data-width="400"}

### Cities with the highest number of FSB recent alumni

```{r,echo=FALSE}
library(ggplot2)

top_10_cities <- head(ranked_offers, 10)

# Create a bar chart for the top 10 cities
ggplot(top_10_cities, aes(x = reorder(city_state, -Offer_Count), y = Offer_Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(x = "City", y = "Job Opportunities") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
The bar graph shows which city offers the most job opportunities for Miami's graduation students. As we can see, Chicago and Cincinnati has the highest number of job opportunities. Consequently, it's more valuable for Mr. Kirk to make more effort on building external relationships with companies in these two cities to raise fund.

```{r}
missing_values <- df_final[is.na(df_final$lat), ]
```


## Column {data-width="400"}
```{r}
city_map_df = data.frame(df_final$lng, df_final$lat, df_final$city_state)
city_map_df = na.omit(city_map_df)
```

```{r}
library(leaflet)

# Create a leaflet map for the top 10 cities
m <- leaflet(data = city_map_df) %>%
  addTiles() %>%
  setView(lng = -98, lat = 39, zoom = 4) %>%
  addCircleMarkers(
    radius = 8,
    color = "blue",
    label = ~df_final.city_state,
    lat = ~df_final.lat,
    lng = ~df_final.lng,
    popup = ~paste("City:", df_final.city_state)
 )
m
```

# Session Info {data-orientation="columns"}

```{r}
sessionInfo()
```

